Evaluating Recommender Behavior For New Users

### 2014-05-07 paper/main.tex
final submission

@@

  {\bf Precision@20}, {\bf MAP@20}, and {\bf Fallout@20} are standard information retrieval metrics.
  As we show later, we found these metrics to not be useful for this evaluation.
  Therefore, to help understand the quality of our recommendations, we also include {\bf MeanRating@20}, and {\bf RMSE@20}.

@@

@@

@@

  The authors would like to express their gratitude towards our colleagues at GroupLens research for their feedback and support while developing this work.
  We would like to specially that Michael Ekstrand for his  important work on the Lenskit recommendation framework.
  This work is supported by NSF grants IIS1017697 and IIS0808692.
  %netfishing and volunteers
  %check with Joe about netfishing.

>>>>

\widowpenalty=3000

@@

  {\bf Precision@20}, {\bf MAP@20}, and {\bf Fallout@20} are standard information retrieval metrics.
  As we show later, we found these metrics to not be useful for this evaluation.
  Therefore, to help understand the quality of our recommendations, we also include MeanRating@20, and RMSE@20.

@@

\footnotetext[3]{We do not plot UserItemBaseline here as it is equivalent to ItemBaseline on this metric.}

@@

\footnotetext[4]{We do not plot UserUser here as it cannot be reliably measured for this metric.}

@@

  The authors would like to express their gratitude towards our colleagues at GroupLens research for their feedback and support while developing this work.
  We would like to specially thank Michael Ekstrand for his  important work on the Lenskit recommendation framework.
  This work is supported by NSF grants IIS1017697 and IIS0808692.
  %netfishing and volunteers
  %check with Joe about netfishing.
